%&pdflate
\documentclass[10pt]{article}
 \textwidth 15cm
 \oddsidemargin 0.0in 
 \evensidemargin 0.0in 
 \topmargin 0in
 \headheight -0in
 \headsep 0in
 \topskip 0in
 \textheight 23.0cm
 \marginparwidth 0in

\usepackage{titlesec}

\titleformat{\section}
  {\normalfont\Large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]

%%%%%%%%%%%%% REMOVE TO GET PAGE NUMBERS BACK %%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{empty}
\thispagestyle{empty}

\begin{document}

\linespread{1.0}



{\center
{\Large\bf Jacob Wilson \\ Data Scientist \vspace{0.1in} }

\begin{center} 
\begin{tabular*}{1.0\textwidth}%
   {@{\extracolsep{\fill}}lr}
	Tel:   +44 7510385493\\
	Email: Jacobp.willo@gmail.com \\
\end{tabular*}
\end{center}


\addtolength{\itemsep}{-1ex} \addtolength{\topsep}{-1.5ex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%			RESEARCH INTERESTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5

\section*{\bf  Professional Skills}
\begin{center}
\begin{tabular}{c c c c}
{\bf Languages (fluent)}: & Python & SQL & Bash\\
{\bf Languages (basic)}: &  R & JavaScript & Rust\\
{\bf Libraries}:  & Scikit-learn & Tensorflow & Pandas \\
{\bf Cloud \& Deployment}: & AWS & Docker & Apache Airflow\\
{\bf IDEs} & Vim & VsCode & Jupyter Notebook \\
{\bf OS}: & Windows & Arch & Debian \\
{\bf Version control}: & Git

\end{tabular}
\end{center}


\section*{\bf Summary}

I am a creative and driven data scientist with an extensive skillset and possess the obsessive work ethic and curiosity charateristic of a top level data scientist.
I wish to expand my experience with unique and challenging problems that require creative solutions
and lateral thinking. 
\newline
I am critical of my own work and able to find flaws in my own methodology. This allows me to
improve projects continually and produce high quality results.
With an intuitive grasp of mathematics I enjoy breaking down academic concepts into manageable chunks when engaging with stakeholders. 
\newline
I pride myself on clear and concise code that can be easily built upon and remain scalable. 
\newline
I posess excellent time management honed by working two data science jobs and doing a full time open
university degree while still producing high quality work.
Due my flexiblity I am happy to learn or create new technology to complete novel tasks.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%			EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5




\section*{\bf Work Experience}


{\bf PPX consulting}, (Financial consulting Company) [Feb 2022 - Present]
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item My work for PPX consulting is as a consultant. 
\item Role includes a lot of novel work with SMEs and allows for exposure to problems not encountered in bigger companies with more solid infrastructure. 
\item Gained many valuable lessons in indepdent work such as talking to clients to assertain
bussiness needs and having regular contact with stake holders and taking more responsability than when not part of a larger team.

\end{itemize}

{\bf Osprey Flight Solutions}, (Leading company in aviation risk analysis) [Feb 2022 - Dec 2022]
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item My role included conducting research into how to get more from the companies
data and to develop these concepts into products
\item Encompassed the whole data science product
life cycle and allowed me to engage in all aspects from discussing requirements with stakeholders to
solving bussiness problems.
\item Gained valuable skills in working as part of a large data science and back end team.
\item Worked on many high stakes data science projects.
\item Reason for leaving: department redundancy
\end{itemize}

{\bf Armstrong Supplies}, (Ecommerce construction company) 	[Mar 2021 - Feb 2022]
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item I was intergral to business functions and developed many full stack skills while on the job.
\item Orignally employed to be a data analyst and then promoted to a data scientist.
\item Set up and maintained a sustainable data ecosystem involving a variety of
technology such as my own bespoke programs, AWS relational databases and data pipelines.
\item NLP and other machine learning projects to be used for automated repricing.
\item Reason for leaving: Expanding my skillset as I was the only data scientist at the company.
\end{itemize}

{\bf work experience} [pre-2021]
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item I was a performing mentalist in Denmark and England and did part time work in many job roles. This is not strictly relevant to data science however I did get a lot of transferable skills in presentation and communication.
\end{itemize}






\section*{\bf EDUCATION}
\begin{center}  % put inside center environment
\begin{tabular*}{1.0\textwidth}%
   {@{\extracolsep{\fill}}llr}
{\bf Professional Certificate}	& 	IBM Data Science \bf{Coursera}&       2021 \\
{\bf Professional Certificate}	& 	Google Data Analytics \bf{Coursera} & 2021 \\
{\bf Professional Certificate}	& 	  DeepLearning.AI TensorFlow Developer  \bf{Coursera}& 2021 \\
{\bf B.Sc.}	& 	Mathematics and Statistics	\bf{Open University}& 	2020-2024 	\\
		
\end{tabular*}
\end{center} 




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%			PERSONAL
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\renewcommand{\labelitemi}{$\bullet$}

\section*{\bf Personal skills}
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item  Memory Athlete 
\item  Blindfold Chess
\item  Mentalism 
\end{itemize}


\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%	 EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5


\section*{\bf Full Stack Projects}


Tensorflow Model to generate text
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item {\bf Link}: https://github.com/SherllyNeo/lstm\_recurrent\_neural\_network
\item This project is a web app where you feed in a text file and it will train a model that will generate speech based on that text with a few user defined parameters. 
\item {\bf Languages}: Python
\end{itemize}

Automatic Repricer tool for wood
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item {\bf Link}: https://github.com/SherllyNeo/repricer\_tool\_ds
\item This project uses NLP, and deep learning to price wood based on competitors and current market trends. It also stores past price data for analysis and serves it in a dashboard.
\item {\bf Languages}: Python, SQL, JavaScript
\end{itemize}

Predicting book ratings from covers and titles
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item {\bf Link}: https://github.com/SherllyNeo/book\_analysis\_ds
\item This project uses a variety of techniques such as UMAP, vectorisation and T-SNE  to predict book ratings from covers and titles as well as looking at the impact of price and other features.
\item {\bf Languages}: Python, R, SQL
\end{itemize}


Companies House Dashboard
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item {\bf Link}: https://github.com/SherllyNeo/companies\_house\_ds
\item This project collects, stores and analyses a large amount of data from companies house in order to predict the profit and longevity of companies based on scientifically tested metrics. 
\item {\bf Languages}: Python, SQL, Rust, JavaScript, SQL
\end{itemize}



\end{document}
