%&pdflate
\documentclass[10pt]{article}
 \textwidth 15cm
 \oddsidemargin 0.0in
 \evensidemargin 0.0in
 \topmargin 0in
 \headheight -0in
 \headsep 0in
 \topskip 0in
 \textheight 23.0cm
 \marginparwidth 0in

\usepackage{titlesec}

\titleformat{\section}
  {\normalfont\Large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]

%%%%%%%%%%%%% REMOVE TO GET PAGE NUMBERS BACK %%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{empty}
\thispagestyle{empty}

\begin{document}

\linespread{1.0}



{\center
{\Large\bf Jacob Wilson \\ Data Scientist \vspace{0.1in} }

\begin{center}
\begin{tabular*}{1.0\textwidth}%
   {@{\extracolsep{\fill}}lr}
	Tel:   +44 7510385493\\
	Email: Jacobp.willo@gmail.com \\
\end{tabular*}
\end{center}


\addtolength{\itemsep}{-1ex} \addtolength{\topsep}{-1.5ex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%			RESEARCH INTERESTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5

\section*{\bf  Professional Skills}
\begin{center}
\begin{tabular}{c c c c c}
{\bf Languages (fluent)}: & Python & C & SQL & Bash \\
{\bf Languages (basic)}: &  R & JavaScript & Rust\\
{\bf Libraries}:  & Scikit-learn & Tensorflow & Pandas \\
{\bf Cloud \& Deployment}: & AWS & Docker & Azure\\
{\bf IDEs} & Vim & VsCode & Jupyter Notebook \\
{\bf OS}: & Windows & Arch & Debian \\
    {\bf Version control}: & Git 

\end{tabular}
\end{center}


\section*{\bf Summary}

I am a creative and driven data scientist with an extensive skill set and possess the obsessive work ethic and curiosity characteristic of a top level data scientist.
I wish to expand my experience with unique and challenging problems that require creative solutions
and lateral thinking.
\newline
I am critical of my own work and able to find flaws in my own methodology. This allows me to
improve projects continually and produce high quality results.
With an intuitive grasp of mathematics I enjoy breaking down academic concepts into manageable chunks when engaging with stakeholders.
\newline
I pride myself on clear and concise code that can be easily built upon and remain scalable.
\newline
I possess excellent time management honed by working two data science jobs and doing a full time open
university degree while still producing high quality work.
Due my flexibility I am happy to learn or create new technology to complete novel tasks.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%			EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5




\section*{\bf Work Experience}

{\bf Clockwise Offices}, (Office Real Estate) [Feb 2023 - Present]
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item Role started as date integration specialist which included data engineering and directing business decisions in regards to the data ecosystem infrastructure.
\item Role evoled into solutions architect, I took responsability of big project delivery and technical deployments.

\end{itemize}

{\bf PPX consulting}, (Financial consulting Company) [Feb 2022 - Present]
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item My work for PPX consulting is as a consultant.
\item Role includes a lot of novel work with SMEs and allows for exposure to problems not encountered in bigger companies with more solid infrastructure.
\item Gained many valuable lessons in indepdent work such as talking to clients to assertain
bussiness needs and having regular contact with stake holders and taking more responsability than when not part of a larger team.

\end{itemize}

{\bf Osprey Flight Solutions}, (Leading company in aviation risk analysis) [Feb 2022 - Dec 2022]
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item My role included conducting research into how to get more from the companies
data and to develop these concepts into products
\item Encompassed the whole data science product
life cycle and allowed me to engage in all aspects from discussing requirements with stakeholders to
solving bussiness problems.
\item Gained valuable skills in working as part of a large data science and back end team.
\item Worked on many high stakes data science projects.
\item Reason for leaving: department redundancy
\end{itemize}

{\bf Armstrong Supplies}, (E-commerce construction company) 	[Mar 2021 - Feb 2022]
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item I was integral to business functions and developed many full stack skills while on the job.
\item Originally employed to be a data analyst and then promoted to a data scientist.
\item Set up and maintained a sustainable data ecosystem involving a variety of
technology such as my own bespoke programs, AWS relational databases and data pipelines.
\item NLP and other machine learning projects to be used for automated repricing.
\item Reason for leaving: Expanding my skill set as I was the only data scientist at the company.
\end{itemize}

{\bf work experience} [pre-2021]
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item I was a performing mentalist in Denmark and England and did part time work in many job roles. This is not strictly relevant to data science however I did get a lot of transferable skills in presentation and communication.
\end{itemize}






\section*{\bf Education}
\begin{center}  % put inside center environment
\begin{tabular*}{1.0\textwidth}%
   {@{\extracolsep{\fill}}llr}
{\bf Professional Certificate}	& 	IBM Data Science \bf{Coursera}&       2021 \\
{\bf Professional Certificate}	& 	Google Data Analytics \bf{Coursera} & 2021 \\
{\bf Professional Certificate}	& 	  DeepLearning.AI TensorFlow Developer  \bf{Coursera}& 2021 \\
{\bf B.Sc.}	& 	Mathematics and Statistics	\bf{Open University}& 	2020-2024 	\\

\end{tabular*}
\end{center}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%			PERSONAL
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\renewcommand{\labelitemi}{$\bullet$}

\section*{\bf Personal skills}
\begin{itemize}
\setlength{\itemsep}{0.10ex}
\item  Memory Athlete
\item  Blindfold Chess
\item  Mentalism
\end{itemize}


\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%	 EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5


\section*{\bf References}
Richard Mayne Data Science {\bf Team Lead Osprey Flight Solutions} \newline
Tel: +44 7979 522256 \textbar Email: richard.mayne@ospreyfs.com \newline
\newline
Adrian Goodman {\bf CEO 0f PPX Consulting} \newline
Tel: +44 7709 155006 \textbar  Email: adrian@ppxconsulting.co.uk \newline
\newline
Aaron Stretton {\bf Data Manager Armstrong Supplies}\newline
Tel: +44 7538 593363 \textbar  Email: amjstretton@gmail.com





\end{document}
